Workflow

### 2014-07-29 Workflow/Workflow.Rmd
Added Scripts/ to PostProcess.R call.

### Post-process the results
* Run `PostProcess.R -R data_resample/<Source>` on a node of dahl to create:       
    + `Packages/EconData/data/<Source>_Coeffs.rda` and
    + `Packages/EconData/data/<Source>_Fitted.rda`.

>>>>

### Post-process the results
* Run `Scripts/PostProcess.R -R data_resample/<Source>` on a node of dahl to create:       
    + `Packages/EconData/data/<Source>_Coeffs.rda` and
    + `Packages/EconData/data/<Source>_Fitted.rda`.
